R Notebook

### 2021-03-10 eda.Rmd
Work on source EDA

They all look pretty similar actually *except* for South, which seems to be higher priced than the other on average

>>>>

They all look pretty similar actually *except* for South, which seems to be higher priced than the other on average.

## Source

Only 18 levels - let's check the table output:

```{r}
table(streetrx$source)
```

Let's recode some of these:

```{r}
# Recode "missing" values to NA
levels(streetrx$source)[levels(streetrx$source) == ''] <- NA_character_
streetrx$source <- recode_factor(streetrx$source, 'w'=NA_character_,
                                 'Idk'=NA_character_)

levels(streetrx$source)[grepl('bluelight', levels(streetrx$source), fixed=TRUE)] <- 'bluelight'
levels(streetrx$source)[grepl('opiophile', levels(streetrx$source), fixed=TRUE)] <- 'opiophile'
```

There's still work to be done on this one. Ultimately about 1/3 of these values are missing - we might not be able to save it from that.
